---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# ojoslackr

<!-- badges: start -->
<!-- badges: end -->

The goal of ojoslackr is to ...

## Installation

You can install the development version of ojoslackr like so:

```{r}
# install.packages("pak")
# pak::pkg_install("openjusticeok/ojoslackr")
library(ojoslackr)
```

## Reproducible Environment with Nix

This package includes `rix.R` configuration for creating reproducible R environments using [Nix](https://nixos.org/). This ensures that everyone working on the project has exactly the same R version and package versions.

### Prerequisites

1. Install [Nix](https://nixos.org/download.html)
2. Install the rix R package: `install.packages("rix")`

### Usage

```{r}
# Generate Nix environment files
source("rix.R")

# Use runtime environment (for using the package)
# nix-shell default.nix

# Use development environment (for package development, includes RStudio)  
# nix-shell shell.nix
```

The rix configuration creates two environments:
- **Runtime environment** (`default.nix`): Minimal environment for using ojoslackr
- **Development environment** (`shell.nix`): Full environment with RStudio and development tools

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ojoslackr)
## basic example code
```
